Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial_revised_Guillaume.tex
revision of abstract and introduction
I revised the abstract in the main tex file, the introduction in the new
paperbody file, and added two references in the bib file.

\begin{abstract}
We propose a method to continuously 
generalize buildings from a given start map to a smaller-scale goal map.
For the sake of convenience, 
we name the buildings on the start map \emph{original buildings}.
%
For an intermediate scale, 
we aggregate the original buildings that will be too close 
by introducing bridges.
We grow (bridged) original buildings based on buffering 
and simplify the grown buildings.
We take into account the shapes of the buildings 
both at the previous map and goal map to make sure that 
the buildings are always growing.
%
\newline\indent
The advantages of our method are as follows. 
First, the buildings grow continuously 
and, at the same time, are simplified.
Second, right angles of buildings are preserved during growing. 
Third, the distances between buildings are 
always larger than a specified threshold.
We do a case study to show the performances of our method.
\end{abstract}

@@

\input{PaperBody}

>>>>

\begin{abstract}
To enable smooth zooming, we propose a method to continuously 
generalize buildings from a given start map to a smaller-scale goal map, where there are only built-up area polygons instead of individual building polygons.
For the sake of convenience, 
we name the buildings on the start map \emph{original buildings}.
%
For an intermediate scale, 
we aggregate the original buildings that will be too close 
by introducing bridges.
We grow (bridge) original buildings based on buffering 
and simplify the grown buildings.
We take into account the shapes of the buildings 
both at the previous map and goal map to make sure that 
the buildings are always growing.
%
\newline\indent
The advantages of our method are as follows. 
First, the buildings grow continuously 
and, at the same time, are simplified.
Second, right angles of buildings are preserved during growing: the merged buildings still look like buildings. 
Third, the distances between buildings are 
always larger than a specified threshold.
We do a case study to show the performances of our method.
\end{abstract}

@@

\input{PaperBody_revised_Guillaume}

### 2017-09-12 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody_revised_Guillaume.tex
revision of abstract and introduction
I revised the abstract in the main tex file, the introduction in the new
paperbody file, and added two references in the bib file.

Digital maps such as Google Maps and OpenStreetMap 
support zooming by displaying maps at different levels. 
This discrete strategy may results in sudden changes, which annoy users.
To provide better zooming experience, 
we try to produce a sequence of maps 
with small incremental changes from a level to another level.
This process is known as \emph{continuous generalization}.

A way to realize continuous generalization is to use morphing.
Often, a start map and a goal map, 
respectively at a larger scale and a smaller scale, 
are used as input, 
then maps at intermediate scales are produced 
while the start map is morphed to the goal map.
In order to morph, correspondences between two maps need to be defined.
For example, corresponding points between a pair of polylines have been 
investigated based on 
dynamic programming \citep{mnwb-mpstc-08}, 
Delaunay triangulations and binary line generalized tree (BLG-tree)  
\citep{Deng2015},
and simulated annealing \citep{Li2017_Annealing}.
From a point to its corresponding point,
the straight-line trajectory is often used to interpolate.
Using morphing, \citet{Peng2016_Admin} continuously generalized 
administrative boundaries based on compatible triangulations.

Also aiming at continuous generalization,
\citet{Danciger2009} grew polygons when a map was zoomed out. Their method 
preserves polygons' topology, area-rations, and relative positions. 
\citet{Chimani2014_Eat} generated a selection sequence for road network.
They removed one road at each step while keeping the remaining roads connected.
\citet{Peng2017_AStar} computed optimal aggregation sequences 
for land-cover areas.

Buildings are important elements on maps.
Many methods have been proposed to generalize them.
For example, \citet{haunertwolff2010} simplified a set of buildings 
based an integer program.
Their simplification minimizes the number of edges of all the buildings 
and guarantees that the errors are smaller than a user-defined tolerance.
At the same time, no topological conflict is introduced by the simplification.
\citet{Buchin2011_Simp} simplified buildings based on an edge-move operation.
One advantage is that their method preserves orientations of the edges.
\citet{Chaudhry2008} identified the boundaries of urban settlement by
calculating `citeness' based on buildings.
\citet{Li2017_Building} morphed between two buildings at different scales.
They managed to preserve the orthogonal characteristics of buildings.

When users zoom out on digital maps, 
buildings become smaller and the distances between buildings decrease. 
In order to make sure that the information of a map is easily perceived, 
an objective proposed by \citet{Weibel1997}, 
some building should be enlarged
and buildings close to each other should be aggregated.
Also, buildings should be simplified.
We consider the three operations in our continuous generalization.

@@

We find buildings which will be too close at time $t$
and aggregate the buildings in the same group by introducing bridges.
We grow the (bridged) original buildings by buffering with miter joins.
Our building simplification consists of two steps.
The first one is to use dilation and erosion to remove pits and spikes.
The second step is to remove vertices using Imai--Iri algorithm.
To make sure that the intermediate-scale buildings never shrink,
we merge the shape of a building 
with the shape at the previously immediate step. 
Also, we clip the building using the shape on goal map.

Our aggregation is based on growing and some of simplifying. 
So we present the two operators before aggregating.

\subsection{Growing buildings based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering a polygon, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way to
better preserve the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that if a vertex of the 
buffer is more than $\alpha \dtrm{G} (\alpha \ge 1)$
away from the original vertex, 
a \emph{square} join is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
Distance $\dtrm{G}$ is the growth at time $t$.
We denote by $d_\mathrm{G}$ the growth for goal map.
Then we define
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

\subsection{Simplifying grown buildings}
\label{sec:Simplify}
\citet{Damen2008} generalized buildings using morphological operators.
A drawback of this method is that the directions of the buildings have to be 
concerned.
\citet{Meijers2016} simplified buildings 
based on offset curves generated from straight skeletons.
We use a method based on buffering to remove pits and spikes of buildings.
Our method is slightly different than \citet{Meijers2016},
but there is an available library \textsc{Clipper} \citep{Johnson2014} 
for the operations.
\fig\ref{fig:RemovePitAndSpike} illustrates our buffering-based method.
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

At time $t$, we grow buildings with distance $\dtrm{G}$,
dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
and dilate back with distance $\dtrm{E}$.
A problem we may have is that 
a building may be broken by eroding
(see \fig\ref{fig:ErosionBreak} for example).
The reason is that 
some parts of a building may be increased (by growing and dilating) 
with distance $\dtrm{G}+\dtrm{D}$, 
but can be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
If $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
and the building is not thick enough, 
the thin part may disappear.
In order to avoid this problem, we require that
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\end{equation}

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, 
which was used as a length threshold by, for example, 
\citet{Regnauld2001}.
Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
%Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
%$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
%t \cdot \frac{l}{2} M_\mathrm{g} >0$.
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} < \frac{2 d_\mathrm{G}}{l}.
\end{equation}

We wish to remove ``bays'' 
which have ``widths'' less than $r_\mathrm{h} = 2\sqrt{a_\mathrm{h}/\pi}$.
Variable $a_\mathrm{h}$ is the least area for a hole to be presented on map.
Following \citep{Chaudhry2008}, we set $a_\mathrm{h} = 8\,\mathrm{mm}^2$.
Variable $r_\mathrm{h}$ is the radius of such a hole 
supposing that the hole is a circle.
Sometimes, our $\dtrm{D}$ is not large enough to do so 
because of the limitation from \eq\ref{eq:d_Dt}.
We define
\[
\dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
\]

\subsection{Grouping buildings based on buffering}
\label{sec:Group}
%There are many ways to group buildings.
%
%Using MST to group buildings: \citet{Zhang2013, 
%	Cetinkaya2015,Deng2017,Regnauld1996}

Original buildings grow according to time $t$.
We put the original building in the same group if 
they grow to become too close.
We group buildings based on buffering.
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each original building with distance 
		$\dtrm{G}+\dtrm{D}$.		
		(c) Erode the dilated polygons with distance $\dtrm{D}$.
		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
		If two polygons in (d) intersect, 
		the original buildings will be put in the same group 
		because they will become too close at time $t$.
		There two groups according to (d).
		One consists of the single middle building and 
		the surrounding $9$ buildings comprise the other group.
		(e) The result of growing and merging at time $t$ 
		if we use $\dtrm{D}=0$.
		The process of (f), (g), and (h) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		In (f), we manage to remove the bay in (e) by additionally dilating 
		with distance $\dtrm{D}$.
		There is only one group left according to (h).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	%in this example, we used _dblTotalGrow *= 5;
	\label{fig:RemoveBay}
\end{figure*}

@@

>>>>

Digital multi-scale maps such as Google Maps and OpenStreetMap 
support zooming by displaying maps at different levels. 
This discrete strategy may results in sudden changes, which disturb user navigation.
To provide better zooming experience, 
we try to produce a sequence of maps 
with small incremental changes from a level to another level.
This process is known as \emph{continuous generalization}.

A way to achieve continuous generalization is to use morphing.
Often, a start map and a goal map, 
respectively at a larger scale and a smaller scale, 
are used as input, 
then maps at intermediate scales are produced 
while the start map is morphed to the goal map.
In order to morph, correspondences between two maps need to be defined.
For example, corresponding points between a pair of polylines have been 
investigated based on 
dynamic programming \citep{mnwb-mpstc-08}, 
Delaunay triangulations and binary line generalized tree (BLG-tree)  
\citep{Deng2015},
and simulated annealing \citep{Li2017_Annealing}.
From a point to its corresponding point,
a straight-line trajectory is often used to interpolate.
Using morphing, \citet{Peng2016_Admin} continuously generalized 
administrative boundaries based on compatible triangulations. When the number of line features is different in the start and goal maps, a continuous selection is required and \citet{Chimani2014_Eat} proposed to generate a selection sequence applicable for road network.
They removed one road at each step while keeping the remaining roads connected.

These methods are interesting but only work on lines and our problem of building polygon interpolation cannot be achieved by similar morphings. Regarding the continuous generalization of polygon map features,
\citet{Danciger2009} proposed to grow polygons when a map was zoomed out. Their method 
preserves polygons' topology, area-ratios, and relative positions.  In the case where the goal map is an aggregated version of start landcover map, \citet{Peng2017_AStar} computed optimal aggregation sequences for land-cover areas.

Buildings are important elements on maps, many methods have been proposed to generalize them but not necessarily in a continuous way.
For example, \citet{haunertwolff2010} simplified a set of buildings 
based an integer program.
Their simplification minimizes the number of edges of all the buildings 
and guarantees that the errors are smaller than a user-defined tolerance.
At the same time, no topological conflict is introduced by the simplification.
\citet{Buchin2011_Simp} simplified buildings based on an edge-move operation.
One advantage is that their method preserves orientations of the edges.

When users zoom out on digital maps, 
buildings become smaller and the distances between buildings decrease. So simplification is not the only necessary operation, and buildings can also be aggregated to legible enough \cite{Weibel1997}. Several methods were proposed to aggregate buildings while preserving the shape of buildings (right angles remain) \cite{Regnauld2001}, \cite{RegnauldRevell07}, \cite{Damen2008}. These algorithms can be used as inspirations to define a continuous transformation of buildings.

Algorithms were also proposed to create built-up area polygons (that appear in our goal map) from individual building polygons (that appear in our start map). For instance, \citet{Chaudhry2008} identified the boundaries of urban settlement by calculating `citiness' based on buildings. But the method cannot be adapted to provide a continuous transformation from the buildings to the built-up area.

Finally, some papers directly tackle the continuous transformation of buildings when scale is reduced. \citet{Li2017_Building} morphed between two buildings at different scales.
They managed to preserve the orthogonal characteristics of buildings, but their algorithm cannot be used in our case as the goal map does not contain buildings anymore. \citet{Touya17b} proposed a progressive transformation of buildings into a built-up area, where buildings are progressively replaced by the shape of the block they belong to. However, this last algorithm is not continuous enough, as each iteration directly transforms a set of buildings in a block into a polygon that covers the whole block. So there is no existing solution for the continuous generalization of building polygons into built-up area polygons.

@@

We group buildings which will be too close at time $t$
and aggregate the buildings in the same group by introducing bridges.
We grow the buildings by buffering with miter joins.
Our building simplification consists of two steps.
The first one is to use dilation and erosion to remove pits and spikes.
The second step is to remove vertices using Imai--Iri algorithm.
To make sure that the intermediate-scale buildings never shrink,
we merge the shape of a building with the shape at the previously immediate 
step. 
Also, we clip the building using the shape on goal map.

\subsection{Grouping buildings based on buffering}
\label{sec:Group}
There are many ways to group buildings.

Using MST to group buildings: \citet{Zhang2013, 
	Cetinkaya2015,Deng2017,Regnauld1996}

We group buildings based on their buffers
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
		(d) Dilate the polygons in (c) with distance 
		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
		If two polygons in (d) intersect, 
		the original buildings in (a) will be put in the same group 
		because they will become too close at time $t$.
		Until this step, there two groups according to (d), 
		one consists of the single middle building and 
		the other group consists of the surrounding $9$ buildings.
		(e) The result of growing and merging at time $t$ 
		if we use $\dtrm{D}=0$.
		The process of (f), (g), and (h) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		In (f), we manage to remove the bay in (e) by additionally dilating 
		with distance $\dtrm{D}$.
		There is only one group left according to (h).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	%in this example, we used _dblTotalGrow *= 5;
	\label{fig:RemoveBay}
\end{figure*}

@@

\subsection{Growing buildings based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
where $d_\mathrm{G}$ is the growing distance, 
away from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

We denote by $d_\mathrm{G}$ the total growth. The growth at time $t$ is
\begin{equation}
	\label{eq:d_Gt}
	\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}

\subsection{Simplifying grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \citet{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes
(see \fig\ref{fig:RemovePitAndSpike}).

At time $t$, we grow buildings with distance $\dtrm{G}$,
dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
and dilate back with distance $\dtrm{E}$.
A problem we may have is that we may break a building by eroding.
The reason is that 
some parts of a building may be increased (by growing and dilating) 
with distance $\dtrm{G}+\dtrm{D}$, 
but be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
If  $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
and a building is not thick enough, 
the building may be broken into several parts
(see \fig\ref{fig:ErosionBreak}).
In order to avoid this problem, we require that
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\end{equation}

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$
(see \eq\ref{eq:d_epsilont}) so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, which was used as a length threshold by 
\citet{Regnauld2001,Li2004,Basaraner2008}.
Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
\end{equation}

We wish to remove ``bays'' which have ``widths'' less than $2\sqrt{a_h/\pi}$.
\todo{why? more details}
Usually, our $\dtrm{D}$ is not large enough to do so.
We use the upper bound in \eq\ref{eq:d_Dt}, that is,
\[
\dtrm{D} = \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\]
